Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-15 paper/main.tex
restructure supplementals

\begin{itemize}
    \item [text in brackets] can probably be deleted
    \item imo AD and AV can be written as movie and audio-description
\end{itemize}

\noindent Method:

@@

\noindent Discussion
\begin{itemize}
    \item "Lokalisation der PPA" vs. "Antwortverhalten einer vorab definierten
        PPA". Machst wohl das erste, beschreibst es aber als das zweite
    \item Summary / Concluding statement
        (data reuse to present compelling new findings \& conclusions derived
        from published.)
\end{itemize}

\noindent Supplemental Material
\begin{itemize}
    \item restructure (results + discussion AV, then AD)
    \item discuss differences of contrasts (s. Simons comment)
\end{itemize}

\noindent Code Availability
\begin{itemize}
    \item https://www.springernature.com/gp/authors/research-data-policy/data-availability-statements/12330880i
\end{itemize}

\noindent Data Availability
\begin{itemize}
    \item s. other psyinfo paper
\end{itemize}

@@

\subsection{Results}

\subsubsection{Robustness of group results across contrasts}

@@

\subsubsection{control contrasts}

\subsection{Discussion}

\subsubsection{congruencies (PPA, RSC, LOC, others)}

@@

\subsection{negative controls and cross-modal controls}

@@

\todo[inline]{discussion \& concluding statement}

>>>>

\begin{itemize}
    \item text in [brackets] can probably be deleted
    \item imo AD and AV can be written as movie and audio-description
\end{itemize}

\noindent Method

@@

\noindent Discussion
\begin{itemize}
    \item "Lokalisation der PPA" vs. "Antwortverhalten einer vorab definierten
        PPA". Machst wohl das erste, beschreibst es aber als das zweite
\end{itemize}

\noindent Supplemental Material
\begin{itemize}
    \item discuss differences of contrasts (s. Simons comment)?
\end{itemize}

\noindent Data Citations, Code Availability, Data Availability

\begin{itemize}
    \item https://www.springernature.com/gp/authors/research-data-policy/data-availability-statements/12330880i
    \item cf. other Scienctific Data analysis paper
\end{itemize}

@@

\subsection{Congruencies across contrasts}

@@

@@

\subsection{Control contrasts}

@@
